Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-01 chapters/introduction/introduction.tex
minor change

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  In this constraint, we model the camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying horizon
  line is easier because it can be explicitly estimated from the scene
  layout.
  In our work, we create a new method using CNN to estimate the
  prior distribution over the horizon line. We assign a probability to
  each horizon candidate sampled from the prior distribution by
  measuring their consistences with detected vanishing points. We
  present the algorithm details in \chapref{fasthorizon}.  \newline

  \item \textbf{Constraint for Time and Location:}
  In this work, we estimate the probability over the
  capture time and the camera geographic location given the input image.
  Our network has two branches which predict the image
  capture time and the geographic location simultaneously.
  For time estimation, our network is able to predict the
  joint distribution over the month of the year and the UTC hour of the
  day when the input image has been captured.
  For coarse camera geo-localization, We provide two approaches to
  obtain the probability distribution over the camera geographic
  location. Most straightforwardly, our network outputs the discrete
  distribution over the geographic location of the camera. Better
  results can be procured with the image capture time as auxiliary input
  (if it is known).  We present the algorithm details in
  \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Location and Orientation:}
  In our previous method, we present that our algorithm can estimate
  the discrete camera location. The predictions are only approximate
  due to the limitation of the algorithm. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation with overhead imagery.
  %
  We designed a network that can jointly learn the semantic layout of
  the aerial image and its projection to the ground-level perspective.
  When computing the value of the constraint function, feed the aerial
  image of a given location and orientation set to the network. 
  By comparing the aerial-to-ground layout with the real layout of the
  ground image, we are able to measure the consistency of these two as
  the value of our constraint function.
  We present the algorithm details in \chapref{crosstransf}.
  \newline

>>>>

\begin{itemize}[noitemsep]
  \item \textbf{Constraint for Camera Pose:}
  We build the constraint function for camera roll and pitch angles.
  Assuming the intrinsic parameters are known, camera roll and pitch
  angles can be derived from the horizon line position on the image.
  Compared to directly detecting the camera pose, identifying horizon
  line is easier because it can be explicitly estimated from the scene
  layout.
  In our work, we create a convolutional neural network to estimate the
  prior distribution over the horizon line.
  For each horizon line candidate sampled from the prior distribution,
  we assign a consistency score to it by measuring the consistencies of
  vanishing points detected on it.
  The constraint function output is defined as the multiplication of
  the prior probability of the associated horizon line and its
  consistency score.
  We present the algorithm details in \chapref{fasthorizon}.
  \newline

  \item \textbf{Constraint for Time and Location:}
  In this work, we estimate the probability over 
  the camera geographic location and the capture time of the input
  image.
  Our network has two branches that predict the image
  capture time and the geographic location simultaneously.
  For time estimation, our network is able to predict the
  joint distribution over the month of the year and the UTC hour of the
  day when the input image was captured.
  For camera geo-localization, our network outputs the discrete
  distribution over the geographic location of the camera. Better
  results can be procured with the image capture time as auxiliary input
  (if it is known).  
  We present the algorithm details in \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Location and Orientation:}
  The previous algorithm only estimates locations approximately
  due to the limited capacity of the deep neural network. In this
  work, we propose a ground-to-aerial geo-calibration method that can
  further refine the prediction results and estimate the
  camera geo-orientation.
  %
  We designed a network that can jointly learn the semantic layout of
  the aerial image and its projection to the ground-level perspective.
  When computing the value of the constraint function, feed the aerial
  image of a given location and orientation to the network. 
  By comparing the aerial-to-ground layout with the real layout of the
  ground image, we are able to measure the consistency between the two
  and use it as the value of our constraint function.
  We present the algorithm details in \chapref{crosstransf}.
  \newline
